---
title: "Data_analysis"
author: "Harvey"
date: "9/9/2021"
output: html_document
---

```{r setup, include=FALSE}
```
### Prerequisite
```{r }
# import packages
if (!require("brms")) install.packages("brms")
if (!require("knitr")) install.packages("knitr")
if (!require("tidyverse")) install.packages("tidyverse")
if (!require("ggpubr")) install.packages("ggpubr")
library(brms)
library(knitr)
library(dplyr)
library(tidyr)
library(readr)
library(forcats)
library(ggplot2)
library(stringr)
library(ggpubr)
```
### Experiment 1
This section contains the code use to plot figures and perform statistical analysis for experiment 1
#### read dataframe and code variables
```{r cars}
# download the data file from github
data_1<-read_csv("1_stats_ready.csv")
summary(data_1)
# change the data type of the columns
data_1$Parenthesis <- as.factor(data_1$Parenthesis)
data_1$Order <- as.factor(data_1$Order)
data_1$Item <- as.factor(data_1$Item)
data_1$ID <- as.factor (data_1$ID)
data_1$Modal_Label <- as.factor (data_1$Modal_Label)
summary(data_1)
# delete filler items
data_1 <- data_1 %>% filter(!is.na(Order))
# reorder factor for plotting 
data_1 <-  data_1 %>% mutate(Order = fct_relevel(Order,"High","High-Low","Low-High","Low"))
summary(data_1)

```
#### 1.1 Plot
##### 1.1.1 Plot the mean rating score across conditions
```{r }
# Plot the mean rating score across conditions
# calculate the statistics
data_mean <- data_1 %>% group_by(Order,Parenthesis) %>% summarize(mean_rating=mean(Rating),sd_rating=sd(Rating),se=sd(Rating) / sqrt(length(Rating)))
# making a bar plot
ggplot(data=data_mean, mapping= aes(x=Order,y=mean_rating, fill= Parenthesis))+
  geom_bar(stat = "identity",position = "dodge")+
  # geom_col(width = 0.6,stat = "identity",position = "dodge",fill="steelblue")+
  geom_text(aes(label=round(mean_rating,1)),position = position_dodge(0.9) ,vjust=3, color="white", size=3.5)+
  geom_errorbar(aes(ymin=mean_rating-se, ymax=mean_rating+se),width=.5,position=position_dodge(.9))+
  labs(x = "Modal Arrangement Conditions", y = expression(paste("Probability\nRating")))+
  theme(axis.text.x = element_text(color = "grey20", size = 10, angle = 0, hjust = .5, vjust = .5, face = "plain"),
        axis.text.y = element_text(color = "grey20", size = 10, angle = 0, hjust = .5, vjust = .5, face = "plain"),  
        axis.title.x = element_text(color = "grey20", size = 12, angle = 0, hjust = 0.5, vjust = -1.5, face = "plain"),
        axis.title.y = element_text(color = "grey20", size = 12, angle = 0, hjust = -1.5, vjust = 0.5, face = "plain"))
ggsave("bar_plot_exp1_condition.png")

```
##### 1.1.2 plot the probability rating of different epistemic expressions
```{r }
# plot the mean rating score across modals
# preparation for plotting: 
# re-code the modal column so that the high modals always precede the low modals
data_1$modal_recode <- recode(data_1$Modal_Label,may_certainly = "certainly_may", may_definitely = "definitely_may",might_certainly = "certainly_might", might_definitely = "definitely_might", might_probably = "probably_might")
summary(data_1)
# create a column showing what modal each stimuli has
mylist <- NULL
counter <- 1
for (item in data_1$Order){
  if (item == "High") {epistemic_expression <- data_1$modal_recode[counter] %>% str_split("_") %>%
sapply("[", 1)} # split the modal_recode column by "_", and take the first element
  else if (item == "Low") {epistemic_expression <- data_1$modal_recode[counter] %>% str_split("_") %>% sapply("[", 2)} 
  else if (item == "Low-High") {epistemic_expression <- str_c(data_1$modal_recode[counter] %>% str_split("_") %>% sapply("[", 2), data_1$modal_recode[counter] %>% str_split("_") %>%
sapply("[", 1), sep = " ")} 
  else {epistemic_expression <- str_c(data_1$modal_recode[counter] %>% str_split("_") %>% sapply("[", 1), data_1$modal_recode[counter] %>% str_split("_") %>% sapply("[", 2), sep = " ")}
 
counter <- counter +1
mylist <- append(mylist, epistemic_expression)
}
data_1$epistemic_expression <- mylist
```

```{r}
# plot the probability rating of different epistemic expressions
# subset the data leaving only single model conditions
data1_sub <- data_1 %>% filter(Order == "High" | Order == "Low" )
# calculate the statistics
data1_sub_mean <- data1_sub %>% group_by(epistemic_expression) %>% summarize(mean_rating=mean(Rating),sd_rating=sd(Rating),se=sd(Rating) / sqrt(length(Rating)))
# create boxplot for data1_sub_mean
ggplot(data1_sub_mean, mapping= aes(x=fct_rev(fct_reorder(epistemic_expression,mean_rating)),
                                    y=mean_rating))+
  geom_bar(stat = "identity", position = "dodge", fill="steelblue")+
  geom_text(aes(label=round(mean_rating,1)), vjust=3, color="white", size=3.5)+
  geom_errorbar(aes(ymin=mean_rating-se, ymax=mean_rating+se),width=.5,position=position_dodge(.9))+
  labs(x = "Epistemic Modals", y = expression(paste("Probability\nRating")))+
  theme(axis.text.x = element_text(color = "grey20", size = 10, angle = 0, hjust = .5, vjust = .5, face = "plain"),
        axis.text.y = element_text(color = "grey20", size = 10, angle = 0, hjust = .5, vjust = .5, face = "plain"),  
        axis.title.x = element_text(color = "grey20", size = 12, angle = 0, hjust = 0.5, vjust = -1.5, face = "plain"),
        axis.title.y = element_text(color = "grey20", size = 12, angle = 0, hjust = -0.9, vjust = 0.45, face = "plain"))
ggsave("bar_plot_exp1_modals.png")
```
#### 1.2 Statistical testing
##### 1.2.1 Maximal model with high-low condition as the baseline
```{r }
# Since the dependent variable, rating scores, was bounded between 0 and 100, we analyzed the data on the logit scale rather than probability scale.
# re-level condition, rescale the dependent variable (to 0~1)
data_1$Order<- factor(data_1$Order, levels = c("High-Low","Low-High","High","Low"))
data_1$rating_rescale <- data_1$Rating/100

# recode the scale variable in which 1 is coded as 0.999, while 0 is coded as 0.001 (following Verkuilen, Smithson, 2012)
data_1$rating_recode <- recode(data_1$rating_rescale, `1.00` = 0.999, `0.00` = 0.001)

# change the dependent variable into logit 
data_1$rating_logit <- log(data_1$rating_recode/(1-data_1$rating_recode))

```

```{r}
# building a linear regression model with high-low condition as the baseline
brm_max_HL_1 <- brm (rating_logit ~ 1 + Order*Parenthesis + 
                      (1+ Order*Parenthesis|ID) + 
                      (1+ Order*Parenthesis|Item),
                    data = data_1,
                    iter = 5000,
                    control = list(adapt_delta = 0.99),
                    seed = 123)
summary(brm_max_HL_1)

```
```{r}
sum_mod_exp1_1 <- summary(brm_max_HL_1)
write.csv(sum_mod_exp1_1$fixed, "sum_mod_exp1_1.csv")

```

```{r}
# create a table for model output
output <- summary(brm_max_HL_1)$fixed
output <- output[1:5,1:4]
row.names(output) <- c('Intercept', 'Low-High', 'High', 'Low', 'With-Parenthesis')
mytable_exp1_1 <- kable(
  output,
  digits = 2,
  align = c('c','c','c','c','c'),
  format = "latex"
 )
```

##### 1.2.2 Maximal model with Low-High condition as the baseline

```{r}
# building a linear regression model with Low-High condition as the baseline
data_1$Order<- factor(data_1$Order, levels = c("Low-High","High-Low","High","Low"))
brm_max_LH_1 <- brm (rating_logit ~ 1 + Order*Parenthesis + 
                      (1+ Order*Parenthesis|ID) + 
                      (1+ Order*Parenthesis|Item),
                    data = data_1,
                    iter = 5000,
                    control = list(adapt_delta = 0.99),
                    seed = 123)
summary(brm_max_LH_1)
sum_mod_exp1_2 <- summary(brm_max_LH_1)
write.csv(sum_mod_exp1_2$fixed, "sum_mod_exp1_2.csv")

```

```{r}
# create a table for model output
output <- summary(brm_max_LH_1)$fixed
output <- output[1:5,1:4]
row.names(output) <- c('Intercept', 'High-Low', 'High', 'Low', 'With-Parenthesis')
mytable_exp1_2 <- kable(
  output,
  digits = 2,
  align = c('c','c','c','c','c'),
  format = "latex"
 )
```

##### 1.2.3 Maximal model with only single modal conditions
```{r }
# High modal condition as the baseline
data_1_single <- data_1 %>% filter(data_1$Order == "High" | data_1$Order == "Low")
brm_exp1_single <- brm (rating_logit ~ 1 + Order*Parenthesis + 
                      (1+ Order*Parenthesis|ID) + 
                      (1+ Order*Parenthesis|Item),
                    data = data_1_single,
                    iter = 5000,
                    control = list(adapt_delta = 0.99),
                    seed = 123)
summary(brm_exp1_single)
sum_mod_exp1_3 <- summary(brm_exp1_single)
write.csv(sum_mod_exp1_3$fixed, "sum_mod_exp1_3.csv")
# create a table for model output
output <- summary(brm_exp1_single)$fixed
output <- output[,1:4]
row.names(output) <- c('Intercept', 'Low', 'With-Parenthesis', 'Low:Parenthesis')
mytable_exp1_3 <- kable(
  output,
  digits = 2,
  align = c('c','c','c','c','c'),
  format = "latex"
 )
```

```{r}
# Low modal condition as the baseline
data_1_single$Order <- factor(data_1_single$Order, levels = c("Low","High"))
brm_exp1_single_Low <- brm (rating_logit ~ 1 + Order*Parenthesis + 
                      (1+ Order*Parenthesis|ID) + 
                      (1+ Order*Parenthesis|Item),
                    data = data_1_single,
                    iter = 5000,
                    control = list(adapt_delta = 0.99),
                    seed = 123)
summary(brm_exp1_single_Low)
sum_mod_exp1_3_low <- summary(brm_exp1_single_Low)
write.csv(sum_mod_exp1_3_low$fixed, "sum_mod_exp1_3_low.csv")
# create a table for model output
output <- summary(brm_exp1_single_Low)$fixed
output <- output[,1:4]
row.names(output) <- c('Intercept', 'High', 'With-Parenthesis', 'High:Parenthesis')
mytable_exp1_3_low <- kable(
  output,
  digits = 2,
  align = c('c','c','c','c','c'),
  format = "latex"
 )

```
##### 1.2.4 Maximal model with only double modal conditions
```{r }
data_1_double <- data_1 %>% filter(data_1$Order == "High-Low" | data_1$Order == "Low-High")
brm_exp1_double <- brm (rating_logit ~ 1 + Order*Parenthesis + 
                      (1+ Order*Parenthesis|ID) + 
                      (1+ Order*Parenthesis|Item),
                    data = data_1_double,
                    iter = 5000,
                    control = list(adapt_delta = 0.99),
                    seed = 123)
summary(brm_exp1_double)
sum_mod_exp1_4 <- summary(brm_exp1_double)
write.csv(sum_mod_exp1_4$fixed, "sum_mod_exp1_4.csv")

# create a table for model output
output <- summary(brm_exp1_double)$fixed
output <- output[,1:4]
row.names(output) <- c('Intercept', 'High-Low', 'With-Parenthesis', 'High-Low: Parenthesis')
mytable_exp1_4 <- kable(
  output,
  digits = 2,
  align = c('c','c','c','c','c'),
  format = "latex"
 )
```


### Experiment 2
This section contains the code use to plot figures and perform statistical analysis for experiment 2
#### read dataframe and code variables
```{r cars}
# download the data file from github
data_2<-read_csv("2_stats_ready.csv")
summary(data_2)
# change the data type of the columns
data_2$Parenthesis <- as.factor(data_2$Parenthesis)
data_2$Order <- as.factor(data_2$Order)
data_2$Item <- as.factor(data_2$Item)
data_2$ID <- as.factor (data_2$ID)
data_2$Modal_Label <- as.factor (data_2$Modal_Label)
summary(data_2)
# delete filler items
data_2 <- data_2 %>% filter(!is.na(Order))
# reorder factor for plotting 
data_2 <-  data_2 %>% mutate(Order = fct_relevel(Order,"High","High-Low","Low-High","Low"))
summary(data_2)

```

#### 2.1 Plot
##### 2.1.1 Plot the mean rating score across conditions
```{r }
# Plot the mean rating score across conditions
# calculate the statistics
data_mean <- data_2 %>% group_by(Order,Parenthesis) %>% summarize(mean_rating=mean(Rating),sd_rating=sd(Rating),se=sd(Rating) / sqrt(length(Rating)))
# making a bar plot
ggplot(data=data_mean, mapping= aes(x=Order,y=mean_rating, fill= Parenthesis))+
  geom_bar(stat = "identity",position = "dodge")+
  # geom_col(width = 0.6,stat = "identity",position = "dodge",fill="steelblue")+
  geom_text(aes(label=round(mean_rating,1)),position = position_dodge(0.9) ,vjust=3, color="white", size=3.5)+
  geom_errorbar(aes(ymin=mean_rating-se, ymax=mean_rating+se),width=.5,position=position_dodge(.9))+
  labs(x = "Modal Arrangement Conditions", y = expression(paste("Probability\nRating")))+
  theme(axis.text.x = element_text(color = "grey20", size = 10, angle = 0, hjust = .5, vjust = .5, face = "plain"),
        axis.text.y = element_text(color = "grey20", size = 10, angle = 0, hjust = .5, vjust = .5, face = "plain"),  
        axis.title.x = element_text(color = "grey20", size = 12, angle = 0, hjust = 0.5, vjust = -1.5, face = "plain"),
        axis.title.y = element_text(color = "grey20", size = 12, angle = 0, hjust = -1.5, vjust = 0.5, face = "plain"))
ggsave("bar_plot_exp2_condition.png")

```
##### 2.1.2 plot the probability rating of different epistemic expressions
```{r }
# plot the mean rating score across modals
# preparation for plotting: 
# re-code the modal column so that the high modals always precede the low modals
data_2$modal_recode <- recode(data_2$Modal_Label,may_certainly = "certainly_may", may_definitely = "definitely_may",might_certainly = "certainly_might", might_definitely = "definitely_might", might_probably = "probably_might")
summary(data_2)
# create a column showing what modal each stimuli has
mylist <- NULL
counter <- 1
for (item in data_2$Order){
  if (item == "High") {epistemic_expression <- data_2$modal_recode[counter] %>% str_split("_") %>%
sapply("[", 1)} # split the modal_recode column by "_", and take the first element
  else if (item == "Low") {epistemic_expression <- data_2$modal_recode[counter] %>% str_split("_") %>% sapply("[", 2)} 
  else if (item == "Low-High") {epistemic_expression <- str_c(data_2$modal_recode[counter] %>% str_split("_") %>% sapply("[", 2), data_2$modal_recode[counter] %>% str_split("_") %>%
sapply("[", 1), sep = " ")} 
  else {epistemic_expression <- str_c(data_2$modal_recode[counter] %>% str_split("_") %>% sapply("[", 1), data_2$modal_recode[counter] %>% str_split("_") %>% sapply("[", 2), sep = " ")}
 
counter <- counter +1
mylist <- append(mylist, epistemic_expression)
}
data_2$epistemic_expression <- mylist
```

```{r}
# plot the probability rating of different epistemic expressions
# subset the data leaving only single model conditions
data2_sub <- data_2 %>% filter(Order == "High" | Order == "Low" )
# calculate the statistics
data2_sub_mean <- data2_sub %>% group_by(epistemic_expression) %>% summarize(mean_rating=mean(Rating),sd_rating=sd(Rating),se=sd(Rating) / sqrt(length(Rating)))
# create boxplot for data1_sub_mean
ggplot(data2_sub_mean, mapping= aes(x=fct_rev(fct_reorder(epistemic_expression,mean_rating)),
                                    y=mean_rating))+
  geom_bar(stat = "identity", position = "dodge", fill="steelblue")+
  geom_text(aes(label=round(mean_rating,1)), vjust=3, color="white", size=3.5)+
  geom_errorbar(aes(ymin=mean_rating-se, ymax=mean_rating+se),width=.5,position=position_dodge(.9))+
  labs(x = "Epistemic Modals", y = expression(paste("Probability\nRating")))+
  theme(axis.text.x = element_text(color = "grey20", size = 10, angle = 0, hjust = .5, vjust = .5, face = "plain"),
        axis.text.y = element_text(color = "grey20", size = 10, angle = 0, hjust = .5, vjust = .5, face = "plain"),  
        axis.title.x = element_text(color = "grey20", size = 12, angle = 0, hjust = 0.5, vjust = -1.5, face = "plain"),
        axis.title.y = element_text(color = "grey20", size = 12, angle = 0, hjust = -0.9, vjust = 0.45, face = "plain"))
ggsave("bar_plot_exp2_modals.png")
```
#### 2.2 Statistical testing
##### 2.2.1 Maximal model with high-low condition as the baseline
```{r }
# Since the dependent variable, rating scores, was bounded between 0 and 100, we analyzed the data on the logit scale rather than probability scale.
# re-level condition, rescale the dependent variable (to 0~1)
data_2$Order<- factor(data_2$Order, levels = c("High-Low","Low-High","High","Low"))
data_2$rating_rescale <- data_2$Rating/100

# recode the scale variable in which 1 is coded as 0.999, while 0 is coded as 0.001 (following Verkuilen, Smithson, 2012)
data_2$rating_recode <- recode(data_2$rating_rescale, `1.00` = 0.999, `0.00` = 0.001)

# change the dependent variable into logit 
data_2$rating_logit <- log(data_2$rating_recode/(1-data_2$rating_recode))

```

```{r}
# building a linear regression model with high-low condition as the baseline
brm_max_HL_2 <- brm (rating_logit ~ 1 + Order*Parenthesis + 
                      (1+ Order*Parenthesis|ID) + 
                      (1+ Order*Parenthesis|Item),
                    data = data_2,
                    iter = 5000,
                    control = list(adapt_delta = 0.99),
                    seed = 123)
summary(brm_max_HL_2)
sum_mod_exp2_1 <- summary(brm_max_HL_2)
write.csv(sum_mod_exp2_1$fixed, "sum_mod_exp2_1.csv")

# create a table for model output
output <- summary(brm_max_HL_2)$fixed
output <- output[1:5,1:4]
row.names(output) <- c('Intercept', 'Low-High', 'High', 'Low', 'With-Parenthesis')
mytable_exp2_1 <- kable(
  output,
  digits = 2,
  align = c('c','c','c','c','c'),
  format = "latex"
 )
```

##### 2.2.2 Maximal model with Low-High condition as the baseline

```{r}
# building a linear regression model with Low-High condition as the baseline
data_2$Order<- factor(data_2$Order, levels = c("Low-High","High-Low","High","Low"))
brm_max_LH_2 <- brm (rating_logit ~ 1 + Order*Parenthesis + 
                      (1+ Order*Parenthesis|ID) + 
                      (1+ Order*Parenthesis|Item),
                    data = data_2,
                    iter = 5000,
                    control = list(adapt_delta = 0.99),
                    seed = 123)
summary(brm_max_LH_2)
sum_mod_exp2_2 <- summary(brm_max_LH_2)
write.csv(sum_mod_exp2_2$fixed, "sum_mod_exp2_2.csv")

# create a table for model output
output <- summary(brm_max_LH_2)$fixed
output <- output[1:5,1:4]
row.names(output) <- c('Intercept', 'High-Low', 'High', 'Low', 'With-Parenthesis')
mytable_exp2_2 <- kable(
  output,
  digits = 2,
  align = c('c','c','c','c','c'),
  format = "latex"
 )
```

##### 2.2.3 Maximal model with only single modal conditions
```{r }
data_2_single <- data_2 %>% filter(data_2$Order == "High" | data_2$Order == "Low")
brm_exp2_single <- brm (rating_logit ~ 1 + Order*Parenthesis + 
                      (1+ Order*Parenthesis|ID) + 
                      (1+ Order*Parenthesis|Item),
                    data = data_2_single,
                    iter = 5000,
                    control = list(adapt_delta = 0.99),
                    seed = 123)
summary(brm_exp2_single)
sum_mod_exp2_3 <- summary(brm_exp2_single)
write.csv(sum_mod_exp2_3$fixed, "sum_mod_exp2_3.csv")

# create a table for model output
output <- summary(brm_exp2_single)$fixed
output <- output[,1:4]
row.names(output) <- c('Intercept', 'Low', 'With-Parenthesis', 'Low:Parenthesis')
mytable_exp2_3 <- kable(
  output,
  digits = 2,
  align = c('c','c','c','c','c'),
  format = "latex"
 )
```

```{r}
# Low modal condition as the baseline
data_2_single$Order <- factor(data_2_single$Order, levels = c("Low","High"))
brm_exp2_single_Low <- brm (rating_logit ~ 1 + Order*Parenthesis + 
                      (1+ Order*Parenthesis|ID) + 
                      (1+ Order*Parenthesis|Item),
                    data = data_2_single,
                    iter = 5000,
                    control = list(adapt_delta = 0.99),
                    seed = 123)
summary(brm_exp2_single_Low)
sum_mod_exp2_3_low <- summary(brm_exp2_single_Low)
write.csv(sum_mod_exp2_3_low$fixed, "sum_mod_exp2_3_low.csv")
# create a table for model output
output <- summary(brm_exp2_single_Low)$fixed
output <- output[,1:4]
row.names(output) <- c('Intercept', 'High', 'With-Parenthesis', 'High:Parenthesis')
mytable_exp2_3_low <- kable(
  output,
  digits = 2,
  align = c('c','c','c','c','c'),
  format = "latex"
 )


```

##### 2.2.4 Maximal model with only double modal conditions
```{r }
data_2_double <- data_2 %>% filter(data_2$Order == "High-Low" | data_2$Order == "Low-High")
brm_exp2_double <- brm (rating_logit ~ 1 + Order*Parenthesis + 
                      (1+ Order*Parenthesis|ID) + 
                      (1+ Order*Parenthesis|Item),
                    data = data_2_double,
                    iter = 5000,
                    control = list(adapt_delta = 0.99),
                    seed = 123)
summary(brm_exp2_double)
sum_mod_exp2_4 <- summary(brm_exp2_double)
write.csv(sum_mod_exp2_4$fixed, "sum_mod_exp2_4.csv")

# create a table for model output
output <- summary(brm_exp2_double)$fixed
output <- output[,1:4]
row.names(output) <- c('Intercept', 'High-Low', 'With-Parenthesis', 'High-Low: Parenthesis')
mytable_exp2_4 <- kable(
  output,
  digits = 2,
  align = c('c','c','c','c','c'),
  format = "latex"
 )
```
### Experiment 3
This section contains the code use to plot figures and perform statistical analysis for experiment 3
#### read dataframe and code variables
```{r}
# import data
mydata1 <- read_csv("3_stats_ready_single.csv")
mydata2 <- read_csv("3_stats_ready_double.csv")
# change the data type for some of the columns
mydata1$id <- as.factor(mydata1$id)
mydata1$random <- as.factor(mydata1$random)
mydata1$item <- as.factor(mydata1$item)
mydata1$condition <- as.factor(mydata1$condition)
mydata2$id <- as.factor(mydata2$id)
mydata2$random <- as.factor(mydata2$random)
mydata2$item <- as.factor(mydata2$item)
mydata2$condition <- as.factor(mydata2$condition)
# contingency table
table_data1 <- table(mydata1$condition,mydata1$choice)
table_data2 <- table(mydata2$condition,mydata2$choice)
```

#### 3.1 Statistical analysis
```{r }
# building mixed effects logistic linear regression model using brms, no significant difference found in double modal conditions
mod_max <- brm (choice ~ 1 + condition +
                   (1+condition|id) +
                   (1+condition|item),
                 data=mydata2,
                family = bernoulli(link = "logit"),
                iter = 5000, 
                control = list(adapt_delta = 0.99),
                seed = 123)

summary(mod_max)
sum_mod_exp3_double <- summary(mod_max)
write.csv(sum_mod_exp3_double$fixed, "sum_mod_exp3_double.csv")
# create a table for model output
output <- sum_mod_exp3_double$fixed
output <- output[,1:4]
row.names(output) <- c('Intercept', 'Low-High')
mytable_exp3_double <- kable(
  output,
  digits = 2,
  align = c('c','c','c','c','c'),
  format = "latex"
)
```

```{r}
# Run the same model for single modal data
mod_max_single <- brm (choice ~ 1 + condition +
                  (1+condition|id) +
                  (1+condition|item),
                data=mydata1,
                family = bernoulli(link = "logit"),
                iter = 5000, 
                control = list(adapt_delta = 0.99),
                seed = 123)
summary(mod_max_single)
sum_mod_exp3_single <- summary(mod_max_single)
write.csv(sum_mod_exp3_single$fixed, "sum_mod_exp3_single.csv")

# create a table for model output
output <- sum_mod_exp3_single$fixed
output <- output[,1:4]
row.names(output) <- c('Intercept', 'Low')
mytable_exp3_single <- kable(
  output,
  digits = 2,
  align = c('c','c','c','c','c'),
  format = "latex"
)
```
#### 3.2 Plotting
```{r}    
# plotting: double modal conditions 
mydata2$condition_recode <- ifelse(mydata2$condition == "highlow", 1,2)
mydata2$logit <- ifelse(mydata2$condition == "highlow", 0.88,0.61)
g2 <- ggplot(data = mydata2,
       aes(x = condition, y = logit)) +
  geom_point(alpha = .1, size = 2)+
  geom_segment(
    aes(x = 1,y = 0.88, xend = 2,yend = 0.61),
    size = 0.2
  )+
  scale_y_continuous(name="Logit of choosing 'high-low' options", limits=c(0, 10))+
  annotate("text", x = 1.8, y=5, label = "β = -0.27, 95% CI [-0.58, 0.03]")

# plotting: single modal conditions  
mydata1$condition_recode <- ifelse(mydata1$condition == "high", 1,2)
mydata1$logit <- ifelse(mydata1$condition == "high", 5.32,0.26)
g1 <- ggplot(data = mydata1,
       aes(x = condition, y = logit)) +
  geom_point(alpha = .1, size = 2)+
  geom_segment(
    aes(x = 1,y = 5.32, xend = 2,yend = 0.26),
    size = 0.2
  )+
  scale_y_continuous(name="Logit of choosing 'high' options", limits=c(0, 10))+
  annotate("text", x = 1.8, y=5, label = "β = -5.06, 95% CI [-6.66, -3.72]")
ggarrange(g1,g2, ncol = 2)
ggsave("line_plot_exp3.png")

```

