---
title: "Data_analysis"
author: "Harvey"
date: "28/2/2023"
output: html_document
---

```{r setup, include=FALSE}
```
### Prerequisite
```{r }
# import packages
if (!require("brms")) install.packages("brms")
if (!require("knitr")) install.packages("knitr")
if (!require("tidyverse")) install.packages("tidyverse")
if (!require("ggpubr")) install.packages("ggpubr")
library(brms)
library(knitr)
library(dplyr)
library(tidyr)
library(readr)
library(forcats)
library(ggplot2)
library(stringr)
library(ggpubr)
```
### Experiment 1
This section contains the code use to plot figures and perform statistical analysis for experiment 1
#### read dataframe and code variables
```{r cars}
# download the data file from github
data_1<-read_csv("1_stats_ready.csv")
# delete the information of order and parenthetical manipulation in the item column
# as a result the item column refers to the id of each item
itemID <- sub("_.*","",data_1$Item)
data_1$Item <-itemID
itemID <- sub("X","",data_1$Item)
data_1$Item <-itemID
# change the data type of the columns
data_1$Parenthesis <- as.factor(data_1$Parenthesis)
data_1$Order <- as.factor(data_1$Order)
data_1$Item <- as.factor(data_1$Item)
data_1$ID <- as.factor (data_1$ID)
data_1$Modal_Label <- as.factor (data_1$Modal_Label)
# delete filler items
data_1 <- data_1 %>% filter(!is.na(Order))
# reorder factor for plotting 
data_1 <-  data_1 %>% mutate(Order = fct_relevel(Order,"High","High-Low","Low-High","Low"))
summary(data_1)

```
#### 1.1 Plot
##### 1.1.1 Plot the mean rating score across conditions
```{r }
# Plot the mean rating score across conditions
# calculate the statistics
data_mean <- data_1 %>% group_by(Order,Parenthesis) %>% summarize(mean_rating=mean(Rating),sd_rating=sd(Rating),se=sd(Rating) / sqrt(length(Rating)))
# making a bar plot
ggplot(data=data_mean, mapping= aes(x=Order,y=mean_rating, fill= Parenthesis))+
  geom_bar(stat = "identity",position = "dodge")+
  # geom_col(width = 0.6,stat = "identity",position = "dodge",fill="steelblue")+
  geom_text(aes(label=round(mean_rating,1)),position = position_dodge(0.9) ,vjust=3, color="white", size=3.5)+
  geom_errorbar(aes(ymin=mean_rating-se, ymax=mean_rating+se),width=.5,position=position_dodge(.9))+
  labs(x = "Modal Arrangement Conditions", y = expression(paste("Probability\nRating")))+
  theme(axis.text.x = element_text(color = "grey20", size = 10, angle = 0, hjust = .5, vjust = .5, face = "plain"),
        axis.text.y = element_text(color = "grey20", size = 10, angle = 0, hjust = .5, vjust = .5, face = "plain"),  
        axis.title.x = element_text(color = "grey20", size = 12, angle = 0, hjust = 0.5, vjust = -1.5, face = "plain"),
        axis.title.y = element_text(color = "grey20", size = 12, angle = 0, hjust = -1.5, vjust = 0.5, face = "plain"))+
  scale_fill_discrete(name = "Parenthetical\nElement", labels = c("Absent", "Present"))
ggsave("bar_plot_exp1_condition.png")

```
```{r }
# Plot the mean rating score across conditions with each facet being an item
# calculate the statistics
data_mean <- data_1 %>% group_by(Order,Item) %>% summarize(mean_rating=mean(Rating),sd_rating=sd(Rating),se=sd(Rating) / sqrt(length(Rating)))
# making a bar plot
ggplot(data=data_mean, mapping= aes(x=Order,y=mean_rating))+
  geom_bar(stat = "identity",position = "dodge")+
  scale_y_continuous(breaks = seq(from =50, to = 100, by = 20))+
  scale_x_discrete(labels=c("H","HL","LH","L"))+
  # geom_col(width = 0.6,stat = "identity",position = "dodge",fill="steelblue")+
  geom_errorbar(aes(ymin=mean_rating-se, ymax=mean_rating+se),width=.5,position=position_dodge(.9))+
  labs(x = "Modal Arrangement Conditions", y = expression(paste("Probability Rating")))+
  coord_cartesian(ylim = c(50,95))+
facet_wrap("Item",nrow = 4, ncol = 8 )

ggsave("bar_plot_exp1_condition_item.png")

```


##### 1.1.2 plot the probability rating of different epistemic expressions
```{r }
# plot the mean rating score across modals
# preparation for plotting: 
# re-code the modal column so that the high modals always precede the low modals
data_1$modal_recode <- recode(data_1$Modal_Label,may_certainly = "certainly_may", may_definitely = "definitely_may",might_certainly = "certainly_might", might_definitely = "definitely_might", might_probably = "probably_might")
summary(data_1)
# create a column showing what modal each stimuli has
mylist <- NULL
counter <- 1
for (item in data_1$Order){
  if (item == "High") {epistemic_expression <- data_1$modal_recode[counter] %>% str_split("_") %>%
sapply("[", 1)} # split the modal_recode column by "_", and take the first element
  else if (item == "Low") {epistemic_expression <- data_1$modal_recode[counter] %>% str_split("_") %>% sapply("[", 2)} 
  else if (item == "Low-High") {epistemic_expression <- str_c(data_1$modal_recode[counter] %>% str_split("_") %>% sapply("[", 2), data_1$modal_recode[counter] %>% str_split("_") %>%
sapply("[", 1), sep = " ")} 
  else {epistemic_expression <- str_c(data_1$modal_recode[counter] %>% str_split("_") %>% sapply("[", 1), data_1$modal_recode[counter] %>% str_split("_") %>% sapply("[", 2), sep = " ")}
 
counter <- counter +1
mylist <- append(mylist, epistemic_expression)
}
data_1$epistemic_expression <- mylist
```

```{r}
# plot the probability rating of different epistemic expressions
# subset the data leaving only single model conditions
data1_sub <- data_1 %>% filter(Order == "High" | Order == "Low" )
# calculate the statistics
data1_sub_mean <- data1_sub %>% group_by(epistemic_expression) %>% summarize(mean_rating=mean(Rating),sd_rating=sd(Rating),se=sd(Rating) / sqrt(length(Rating)))
# create boxplot for data1_sub_mean
ggplot(data1_sub_mean, mapping= aes(x=fct_rev(fct_reorder(epistemic_expression,mean_rating)),
                                    y=mean_rating))+
  geom_bar(stat = "identity", position = "dodge", fill="steelblue")+
  geom_text(aes(label=round(mean_rating,1)), vjust=3, color="white", size=3.5)+
  geom_errorbar(aes(ymin=mean_rating-se, ymax=mean_rating+se),width=.5,position=position_dodge(.9))+
  labs(x = "Epistemic Modals", y = expression(paste("Probability\nRating")))+
  theme(axis.text.x = element_text(color = "grey20", size = 10, angle = 0, hjust = .5, vjust = .5, face = "plain"),
        axis.text.y = element_text(color = "grey20", size = 10, angle = 0, hjust = .5, vjust = .5, face = "plain"),  
        axis.title.x = element_text(color = "grey20", size = 12, angle = 0, hjust = 0.5, vjust = -1.5, face = "plain"),
        axis.title.y = element_text(color = "grey20", size = 12, angle = 0, hjust = -0.9, vjust = 0.45, face = "plain"))
ggsave("bar_plot_exp1_modals.png")
```
#### 1.2 Statistical analysis

```{r }
# Since the dependent variable, rating scores, was bounded between 0 and 100, we analyzed the data on the logit scale rather than probability scale.
# re-level condition, rescale the dependent variable (to 0~1)

data_1$rating_rescale <- data_1$Rating/100

# recode the scale variable in which 1 is coded as 0.999, while 0 is coded as 0.001 (following Verkuilen, Smithson, 2012)
data_1$rating_recode <- recode(data_1$rating_rescale, `1.00` = 0.999, `0.00` = 0.001)

# change the dependent variable into logit 
data_1$rating_logit <- log(data_1$rating_recode/(1-data_1$rating_recode))

```

##### 1.2.1 The compositionality of nested epistemic expressions and the order effect

This section contains statistical analysis with regard to two research questions 1) the compositionality of the nested epistemic expressions: what is the relation between the meaning of a nested epistemic expression and the
meaning of the component modals 2) the order effect: whether or not the order of the two modals has an effect on comprehenders’ interpretation of the nested expressions.

To answer these questions, we build models to test the effect of different modal combinations ("High-Low","Low-High","High","Low") on the probability rating. The first model uses "High-Low" combination as the baseline.

```{r}
# building a linear regression model with high-low condition as the baseline
data_1$Order<- factor(data_1$Order, levels = c("High-Low","Low-High","High","Low"))

brm_exp1_q12_1 <- brm (rating_logit ~ 1 + Order + 
                      (1+ Order|ID) + 
                      (1+ Order|Item),
                    data = data_1,
                    iter = 8000,
                    control = list(adapt_delta = 0.99),
                    seed = 1)
summary(brm_exp1_q12_1)
# save the output of fixed effect
write.csv(summary(brm_exp1_q12_1)$fixed, "brm_exp1_q12_1.csv")

# create a latex table for model output
output <- summary(brm_exp1_q12_1)$fixed
output <- output[1:4,1:4]
row.names(output) <- c('Intercept', 'Low-High', 'High', 'Low')
tb_exp1_q12_1 <- kable(
  output,
  digits = 2,
  align = c('c','c','c','c','c'),
  format = "latex"
 )
# save the latex table output in a text file
writeLines(tb_exp1_q12_1,"tb_exp1_q12_1.txt")
```

The second model follows the same structure but uses "Low-High" combination as the baseline

```{r}
# building a linear regression model with Low-High condition as the baseline
data_1$Order<- factor(data_1$Order, levels = c("Low-High","High-Low","High","Low"))

brm_exp1_q12_2 <- brm (rating_logit ~ 1 + Order + 
                      (1+ Order|ID) + 
                      (1+ Order|Item),
                    data = data_1,
                    iter = 8000,
                    control = list(adapt_delta = 0.99),
                    seed = 1)
summary(brm_exp1_q12_2)

# save the output of fixed effect
write.csv(summary(brm_exp1_q12_2)$fixed, "brm_exp1_q12_2.csv")

# create a latex table for model output
output <- summary(brm_exp1_q12_2)$fixed
output <- output[1:4,1:4]
row.names(output) <- c('Intercept', 'High-Low', 'High', 'Low')
tb_exp1_q12_2 <- kable(
  output,
  digits = 2,
  align = c('c','c','c','c','c'),
  format = "latex"
 )
# save the latex table output in a text file
writeLines(tb_exp1_q12_2,"tb_exp1_q12_2.txt")

```

##### 1.2.2 The effect of word order with regard to the parenthesis

This section analyzes the effect of modal word order with regard to the presence of parenthesis, answering the following question: does the distance of the component modals influence the way in which nested epistemic expressions are processed?

To answer this question, we build statistical models with nested modal data only. The first model includes modal order and the presence of the parenthesis and their interaction as fixed effects, while participants and items are treated as random effects. The second model follows almost the same structure, but the interaction is dropped. A model comparison is conducted to test if the data is better explained with an interaction.

```{r}

# subset the data frame keeping only the data in nested modal conditions

data_1_double <- data_1 %>% filter(data_1$Order == "Low-High" | data_1$Order == "High-Low")

# set "High-Low" and the absence of the parentheticals as the baselines for comparision

data_1_double$Order<- factor(data_1_double$Order, levels = c("High-Low","Low-High"))
data_1_double$Parenthesis <- factor(data_1_double$Parenthesis, levels = c("No","Yes"))

# the first model includes the interaction between order and parenthesis
brm_exp1_q3_1 <- brm (rating_logit ~ 1 + Order*Parenthesis + 
                      (1+ Order*Parenthesis|ID) + 
                      (1+ Order*Parenthesis|Item),
                    data = data_1_double,
                    iter = 8000,
                    control = list(adapt_delta = 0.99),
                    seed = 1)
summary(brm_exp1_q3_1)

# save the output of fixed effect
write.csv(summary(brm_exp1_q3_1)$fixed, "brm_exp1_q3_1.csv")

# create a latex table for model output
output <- summary(brm_exp1_q3_1)$fixed
output <- output[1:4,1:4]
row.names(output) <- c('Intercept', 'Low-High', 'With-Parenthetical', 'Low-High-With-Parenthetical')
tb_exp1_q3_1 <- kable(
  output,
  digits = 2,
  align = c('c','c','c','c','c'),
  format = "latex"
 )
# save the latex table output in a text file
writeLines(tb_exp1_q3_1,"tb_exp1_q3_1.txt")


```

### Experiment 2
This section contains the code use to plot figures and perform statistical analysis for experiment 2
#### read dataframe and code variables
```{r cars}
# download the data file from github
data_2<-read_csv("2_stats_ready.csv")
# delete the information of order and parenthetical manipulation in the item column
# as a result the item column refers to the id of each item
itemID2 <- sub("_.*","",data_2$Item)
data_2$Item <- itemID2
# change the data type of the columns
data_2$Parenthesis <- as.factor(data_2$Parenthesis)
data_2$Order <- as.factor(data_2$Order)
data_2$Item <- as.factor(data_2$Item)
data_2$ID <- as.factor (data_2$ID)
data_2$Modal_Label <- as.factor (data_2$Modal_Label)
# delete filler items
data_2 <- data_2 %>% filter(!is.na(Order))
# reorder factor for plotting 
data_2 <-  data_2 %>% mutate(Order = fct_relevel(Order,"High","High-Low","Low-High","Low"))
summary(data_2)

```

#### 2.1 Plot
##### 2.1.1 Plot the mean rating score across conditions
```{r }
# Plot the mean rating score across conditions
# calculate the statistics
data_mean <- data_2 %>% group_by(Order,Parenthesis) %>% summarize(mean_rating=mean(Rating),sd_rating=sd(Rating),se=sd(Rating) / sqrt(length(Rating)))
# making a bar plot
ggplot(data=data_mean, mapping= aes(x=Order,y=mean_rating, fill= Parenthesis))+
  geom_bar(stat = "identity",position = "dodge")+
  # geom_col(width = 0.6,stat = "identity",position = "dodge",fill="steelblue")+
  geom_text(aes(label=round(mean_rating,1)),position = position_dodge(0.9) ,vjust=3, color="white", size=3.5)+
  geom_errorbar(aes(ymin=mean_rating-se, ymax=mean_rating+se),width=.5,position=position_dodge(.9))+
  labs(x = "Modal Arrangement Conditions", y = expression(paste("Probability\nRating")))+
  theme(axis.text.x = element_text(color = "grey20", size = 10, angle = 0, hjust = .5, vjust = .5, face = "plain"),
        axis.text.y = element_text(color = "grey20", size = 10, angle = 0, hjust = .5, vjust = .5, face = "plain"),  
        axis.title.x = element_text(color = "grey20", size = 12, angle = 0, hjust = 0.5, vjust = -1.5, face = "plain"),
        axis.title.y = element_text(color = "grey20", size = 12, angle = 0, hjust = -1.5, vjust = 0.5, face = "plain"))+
  scale_fill_discrete(name = "Parenthetical\nElement", labels = c("Absent", "Present"))
  
ggsave("bar_plot_exp2_condition.png")

```
```{r }
# Plot the mean rating score across conditions with each facet being an item
# calculate the statistics
data_mean2 <- data_2 %>% group_by(Order,Item) %>% summarize(mean_rating=mean(Rating),sd_rating=sd(Rating),se=sd(Rating) / sqrt(length(Rating)))
# making a bar plot
ggplot(data=data_mean2, mapping= aes(x=Order,y=mean_rating))+
  geom_bar(stat = "identity",position = "dodge")+
  scale_y_continuous(breaks = seq(from =50, to = 100, by = 20))+
  scale_x_discrete(labels=c("H","HL","LH","L"))+
  # geom_col(width = 0.6,stat = "identity",position = "dodge",fill="steelblue")+
  geom_errorbar(aes(ymin=mean_rating-se, ymax=mean_rating+se),width=.5,position=position_dodge(.9))+
  labs(x = "Modal Arrangement Conditions", y = expression(paste("Probability Rating")))+
  coord_cartesian(ylim = c(45,95))+
facet_wrap("Item",nrow = 4, ncol = 8 )

ggsave("bar_plot_exp1_condition_item2.png")

```

##### 2.1.2 plot the probability rating of different epistemic expressions
```{r }
# plot the mean rating score across modals
# preparation for plotting: 
# re-code the modal column so that the high modals always precede the low modals
data_2$modal_recode <- recode(data_2$Modal_Label,may_certainly = "certainly_may", may_definitely = "definitely_may",might_certainly = "certainly_might", might_definitely = "definitely_might", might_probably = "probably_might")
summary(data_2)
# create a column showing what modal each stimuli has
mylist <- NULL
counter <- 1
for (item in data_2$Order){
  if (item == "High") {epistemic_expression <- data_2$modal_recode[counter] %>% str_split("_") %>%
sapply("[", 1)} # split the modal_recode column by "_", and take the first element
  else if (item == "Low") {epistemic_expression <- data_2$modal_recode[counter] %>% str_split("_") %>% sapply("[", 2)} 
  else if (item == "Low-High") {epistemic_expression <- str_c(data_2$modal_recode[counter] %>% str_split("_") %>% sapply("[", 2), data_2$modal_recode[counter] %>% str_split("_") %>%
sapply("[", 1), sep = " ")} 
  else {epistemic_expression <- str_c(data_2$modal_recode[counter] %>% str_split("_") %>% sapply("[", 1), data_2$modal_recode[counter] %>% str_split("_") %>% sapply("[", 2), sep = " ")}
 
counter <- counter +1
mylist <- append(mylist, epistemic_expression)
}
data_2$epistemic_expression <- mylist
```

```{r}
# plot the probability rating of different epistemic expressions
# subset the data leaving only single model conditions
data2_sub <- data_2 %>% filter(Order == "High" | Order == "Low" )
# calculate the statistics
data2_sub_mean <- data2_sub %>% group_by(epistemic_expression) %>% summarize(mean_rating=mean(Rating),sd_rating=sd(Rating),se=sd(Rating) / sqrt(length(Rating)))
# create boxplot for data1_sub_mean
ggplot(data2_sub_mean, mapping= aes(x=fct_rev(fct_reorder(epistemic_expression,mean_rating)),
                                    y=mean_rating))+
  geom_bar(stat = "identity", position = "dodge", fill="steelblue")+
  geom_text(aes(label=round(mean_rating,1)), vjust=3, color="white", size=3.5)+
  geom_errorbar(aes(ymin=mean_rating-se, ymax=mean_rating+se),width=.5,position=position_dodge(.9))+
  labs(x = "Epistemic Modals", y = expression(paste("Probability\nRating")))+
  theme(axis.text.x = element_text(color = "grey20", size = 10, angle = 0, hjust = .5, vjust = .5, face = "plain"),
        axis.text.y = element_text(color = "grey20", size = 10, angle = 0, hjust = .5, vjust = .5, face = "plain"),  
        axis.title.x = element_text(color = "grey20", size = 12, angle = 0, hjust = 0.5, vjust = -1.5, face = "plain"),
        axis.title.y = element_text(color = "grey20", size = 12, angle = 0, hjust = -0.9, vjust = 0.45, face = "plain"))
ggsave("bar_plot_exp2_modals.png")
```
#### 2.2 Statistical testing

```{r }
# Since the dependent variable, rating scores, was bounded between 0 and 100, we analyzed the data on the logit scale rather than probability scale.
# re-level condition, rescale the dependent variable (to 0~1)
data_2$Order<- factor(data_2$Order, levels = c("High-Low","Low-High","High","Low"))
data_2$rating_rescale <- data_2$Rating/100

# recode the scale variable in which 1 is coded as 0.999, while 0 is coded as 0.001 (following Verkuilen, Smithson, 2012)
data_2$rating_recode <- recode(data_2$rating_rescale, `1.00` = 0.999, `0.00` = 0.001)

# change the dependent variable into logit 
data_2$rating_logit <- log(data_2$rating_recode/(1-data_2$rating_recode))

```

##### 2.2.1 The compositionality of nested epistemic expressions and the order effect

This section contains statistical analysis with regard to two research questions 1) the compositionality of the nested epistemic expressions: what is the relation between the meaning of a nested epistemic expression and the
meaning of the component modals 2) the order effect: whether or not the order of the two modals has an effect on comprehenders’ interpretation of the nested expressions.

To answer these questions, we build models to test the effect of different modal combinations ("High-Low","Low-High","High","Low") on the probability rating. The first model uses "High-Low" combination as the baseline.

```{r}
# building a linear regression model with high-low condition as the baseline
data_2$Order<- factor(data_2$Order, levels = c("High-Low","Low-High","High","Low"))

brm_exp2_q12_1 <- brm (rating_logit ~ 1 + Order + 
                      (1+ Order|ID) + 
                      (1+ Order|Item),
                    data = data_2,
                    iter = 8000,
                    control = list(adapt_delta = 0.99),
                    seed = 1)
summary(brm_exp2_q12_1)
# save the output of fixed effect
write.csv(summary(brm_exp2_q12_1)$fixed, "brm_exp2_q12_1.csv")

# create a latex table for model output
output <- summary(brm_exp2_q12_1)$fixed
output <- output[1:4,1:4]
row.names(output) <- c('Intercept', 'Low-High', 'High', 'Low')
tb_exp2_q12_1 <- kable(
  output,
  digits = 2,
  align = c('c','c','c','c','c'),
  format = "latex"
 )
# save the latex table output in a text file
writeLines(tb_exp2_q12_1,"tb_exp2_q12_1.txt")
```

The second model follows the same structure but uses "Low-High" combination as the baseline

```{r}
# building a linear regression model with Low-High condition as the baseline
data_2$Order<- factor(data_2$Order, levels = c("Low-High","High-Low","High","Low"))

brm_exp2_q12_2 <- brm (rating_logit ~ 1 + Order + 
                      (1+ Order|ID) + 
                      (1+ Order|Item),
                    data = data_2,
                    iter = 12000,
                    warmup = 6000,
                    control = list(adapt_delta = 0.99, max_treedepth = 15),
                    seed = 1)
summary(brm_exp2_q12_2)

# save the output of fixed effect
write.csv(summary(brm_exp2_q12_2)$fixed, "brm_exp2_q12_2.csv")

# create a latex table for model output
output <- summary(brm_exp2_q12_2)$fixed
output <- output[1:4,1:4]
row.names(output) <- c('Intercept', 'High-Low', 'High', 'Low')
tb_exp2_q12_2 <- kable(
  output,
  digits = 2,
  align = c('c','c','c','c','c'),
  format = "latex"
 )
# save the latex table output in a text file
writeLines(tb_exp2_q12_2,"tb_exp2_q12_2.txt")

```


##### 2.2.2 The effect of word order with regard to the parenthesis

This section analyzes the effect of modal word order with regard to the presence of parenthesis, answering the following question: does the distance of the component modals influence the way in which nested epistemic expressions are processed?

To answer this question, we build statistical models with nested modal data only. The first model includes modal order and the presence of the parenthesis and their interaction as fixed effects, while participants and items are treated as random effects. The second model follows almost the same structure, but the interaction is dropped. A model comparison is conducted to test if the data is better explained with an interaction.

```{r}

# subset the data frame keeping only the data in nested modal conditions

data_2_double <- data_2 %>% filter(data_2$Order == "Low-High" | data_2$Order == "High-Low")

# set "High-Low" and the absence of the parentheticals as the baselines for comparision

data_2_double$Order<- factor(data_2_double$Order, levels = c("High-Low","Low-High"))
data_2_double$Parenthesis <- factor(data_2_double$Parenthesis, levels = c("No","Yes"))

# the first model includes the interaction between order and parenthesis
brm_exp2_q3_1 <- brm (rating_logit ~ 1 + Order*Parenthesis + 
                      (1+ Order*Parenthesis|ID) + 
                      (1+ Order*Parenthesis|Item),
                    data = data_2_double,
                    iter = 8000,
                    control = list(adapt_delta = 0.99),
                    seed = 1)
summary(brm_exp2_q3_1)

# save the output of fixed effect
write.csv(summary(brm_exp2_q3_1)$fixed, "brm_exp2_q3_1.csv")

# create a latex table for model output
output <- summary(brm_exp2_q3_1)$fixed
output <- output[1:4,1:4]
row.names(output) <- c('Intercept', 'Low-High', 'With-Parenthetical', 'Low-High-With-Parenthetical')
tb_exp2_q3_1 <- kable(
  output,
  digits = 2,
  align = c('c','c','c','c','c'),
  format = "latex"
 )
# save the latex table output in a text file
writeLines(tb_exp2_q3_1,"tb_exp2_q3_1.txt")


```


### Experiment 3
This section contains the code use to plot figures and perform statistical analysis for experiment 3
#### read dataframe and code variables
```{r}
# import data
mydata1 <- read_csv("3_stats_ready_single.csv")
mydata2 <- read_csv("3_stats_ready_double.csv")
# change the data type for some of the columns
mydata1$id <- as.factor(mydata1$id)
mydata1$random <- as.factor(mydata1$random)
mydata1$item <- as.factor(mydata1$item)
mydata1$condition <- as.factor(mydata1$condition)
mydata2$id <- as.factor(mydata2$id)
mydata2$random <- as.factor(mydata2$random)
mydata2$item <- as.factor(mydata2$item)
mydata2$condition <- as.factor(mydata2$condition)
# contingency table
table_data1 <- table(mydata1$condition,mydata1$choice)
table_data2 <- table(mydata2$condition,mydata2$choice)
```

#### 3.1 Statistical analysis
```{r }
# building mixed effects logistic linear regression model using brms, no significant difference found in double modal conditions
mod_max <- brm (choice ~ 1 + condition +
                   (1+condition|id) +
                   (1+condition|item),
                 data=mydata2,
                family = bernoulli(link = "logit"),
                iter = 5000, 
                control = list(adapt_delta = 0.99),
                seed = 123)

summary(mod_max)
sum_mod_exp3_double <- summary(mod_max)
write.csv(sum_mod_exp3_double$fixed, "sum_mod_exp3_double.csv")
# create a table for model output
output <- sum_mod_exp3_double$fixed
output <- output[,1:4]
row.names(output) <- c('Intercept', 'Low-High')
mytable_exp3_double <- kable(
  output,
  digits = 2,
  align = c('c','c','c','c','c'),
  format = "latex"
)
```

```{r}
# Run the same model for single modal data
mod_max_single <- brm (choice ~ 1 + condition +
                  (1+condition|id) +
                  (1+condition|item),
                data=mydata1,
                family = bernoulli(link = "logit"),
                iter = 5000, 
                control = list(adapt_delta = 0.99),
                seed = 123)
summary(mod_max_single)
sum_mod_exp3_single <- summary(mod_max_single)
write.csv(sum_mod_exp3_single$fixed, "sum_mod_exp3_single.csv")

# create a table for model output
output <- sum_mod_exp3_single$fixed
output <- output[,1:4]
row.names(output) <- c('Intercept', 'Low')
mytable_exp3_single <- kable(
  output,
  digits = 2,
  align = c('c','c','c','c','c'),
  format = "latex"
)
```
#### 3.2 Plotting
```{r}    
# plotting: double modal conditions 
mydata2$condition_recode <- ifelse(mydata2$condition == "highlow", 1,2)
mydata2$logit <- ifelse(mydata2$condition == "highlow", 0.88,0.61)
g2 <- ggplot(data = mydata2,
       aes(x = condition, y = logit)) +
  geom_point(alpha = .1, size = 2)+
  geom_segment(
    aes(x = 1,y = 0.88, xend = 2,yend = 0.61),
    size = 0.2
  )+
  scale_y_continuous(name="Logit of choosing 'high-low' options", limits=c(0, 10))+
  annotate("text", x = 1.8, y=5, label = "β = -0.27, 95% CI [-0.57, 0.03]")

# plotting: single modal conditions  
mydata1$condition_recode <- ifelse(mydata1$condition == "high", 1,2)
mydata1$logit <- ifelse(mydata1$condition == "high", 5.31,0.25)
g1 <- ggplot(data = mydata1,
       aes(x = condition, y = logit)) +
  geom_point(alpha = .1, size = 2)+
  geom_segment(
    aes(x = 1,y = 5.31, xend = 2,yend = 0.25),
    size = 0.2
  )+
  scale_y_continuous(name="Logit of choosing 'high' options", limits=c(0, 10))+
  annotate("text", x = 1.8, y=5, label = "β = -5.06, 95% CI [-6.65, -3.71]")
ggarrange(g1,g2, ncol = 2)
ggsave("line_plot_exp3.png")

```

